---
title: "Package passport"
author: "Michele Stefano Altieri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package passport}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---
  
```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(tidy = FALSE, comment = "#>")
```

# passport - Manage access credentials with R

[![Build Status](https://travis-ci.org/msaltieri/passport.svg?branch=master)](https://travis-ci.org/msaltieri/passport)

> *Copyright 2017 [Michele Stefano Altieri](http://github.com/msaltieri).
> Licensed under the MIT license.*

`passport` lets you manage username and password for databases or web services
in order to provide full access to external resources without exposing
credential within the code.

## Table of contents

- [Installation](#install)
- [How to use](#usage)

<h2 id="install">Installation</h2>

`passport` is not yet available through CRAN, but you can install the latest development version from GitHub:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("msaltieri/passport")
```

<h2 id="usage">How to use</h2>

You can handle a simple password repository by running

```{r eval=FALSE}
library(passport)
my_vault <- new_vault(tempfile())
my_vault
```

Then you can add your first test credentials by running

```{r eval=FALSE}
proxy1_set <- list(service   = "postgres",
                   host      = "my_istance.dbserver.com",
                   port      = "5432",
                   username  = "admin",
                   password  = "12345")
vault_add(my_vault, proxy1_set)
my_vault
```

Then maybe you can even add a second set of credentials
    
```{r eval=FALSE}
proxy2_set <- list(service   = "data_provider",
                   host      = "ftp://download.data_provider.com",
                   port      = "22",
                   username  = "alice",
                   password  = "67890")
vault_add(my_vault, proxy2_set)
my_vault
```
    
It's now easy to retrieve data from the vault by service name

```{r eval=FALSE}
vault_get(my_vault, "postgres")
```    
    
Or maybe showing all the credential stored in the vault with just one command

```{r eval=FALSE}
vault_getall(my_vault)
```

If you need to delete a specific set of credentials, just run

```{r eval=FALSE}
vault_rm(my_vault, "postgres")
my_vault
```

You can erase completely the vault and all the data stored inside by running

```{r eval=FALSE}
vault_delete(my_vault)
my_vault
```
